Exploring mathematical objects from custom-tailored mathematical universes

### 2020-01-08 paper-filmat.tex
to do
typo

Firstly, toposes are more general than models of set theory. By definition, a
model of~$\mathbf{ZFC}$ will always satisfy the axioms of~$\mathbf{ZFC}$; in
contrast, most toposes do not even validate the law of excluded middle, much
less so the axiom of choice (which implies the law of excluded middle in
presence of the remaining axioms of intuitionistic Zermelo--Fraenkel set
theory~\cite{XXX}). This failure of classicality is often for interesting
geometric or algebraic reasons instead of because of logical issues, as will be
detailed in Section~\ref{several-toposes}.

@@

\subsection{``There are infinitely many primes.''} A first-order formalization
of this statement is ``for any natural number~$n$, there is a natural
number~$p$ which is greater than~$n$'', and is known to be true in the standard
topos by any of the many proofs of this fact.

@@

>>>>

Firstly, toposes are more general than models of set theory. By definition, a
model of~$\mathbf{ZFC}$ will always satisfy the axioms of~$\mathbf{ZFC}$; in
contrast, most toposes do not even validate the law of excluded middle, much
less so the axiom of choice (which implies the law of excluded middle in
presence of the remaining axioms of intuitionistic Zermelo--Fraenkel set
theory~\cite{XXX}). This failure of classicality is often for interesting
geometric or algebraic reasons instead of logical issues, as will be
detailed in Section~\ref{several-toposes}.

@@

\subsection{``There are infinitely many primes.''} A first-order formalization
of this statement is ``for any natural number~$n$, there is a prime
number~$p$ which is greater than~$n$'', and is known to be true in the standard
topos by any of the many proofs of this fact.

@@

Mention forcing
